### 2022-10-20 README.Rmd
readme link update

This repository contains the R code and other materials for the [preprint](https://doi.org/10.26434/chemrxiv-2022-rtzqm) "Sodium silicate and hexametaphosphate promote the release of (oxyhydr)oxide nanoparticles from corroding iron". When rendering the .Rmd file, run `R/render_paper.R` to get the proper formatting for Arabic numeral citations.

>>>>

This repository contains the R code and other materials for the [paper](https://doi.org/10.1039/D2VA00199C) (and [preprint](https://doi.org/10.26434/chemrxiv-2022-rtzqm-v3)) "Sodium silicate and hexametaphosphate promote the release of (oxyhydr)oxide nanoparticles from corroding iron". When rendering the .Rmd file, run `R/render_paper.R` to get the proper formatting for Arabic numeral citations.
